---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# exportreg

`exportreg` turns a named list of regression models into publication-ready
tables for export to **Excel** and **LaTeX**, with first-class support for
`fixest` models (`feols`, `fepois`, `feiv`).

## Installation

```r
# install.packages("remotes")
remotes::install_github("vicentelopez/exportreg")
```

## Minimal example

### Simulate data and fit models

```{r models}
library(exportreg)
library(fixest)

set.seed(42)
n <- 200
dat <- data.frame(
  log_wage  = rnorm(n, mean = 2.8, sd = 0.5),
  educ      = sample(8:20, n, replace = TRUE),
  exper     = sample(1:30, n, replace = TRUE),
  female    = rbinom(n, 1, 0.45),
  firm_id   = sample(1:20, n, replace = TRUE)
)

m1 <- feols(log_wage ~ educ + exper          | firm_id, data = dat)
m2 <- feols(log_wage ~ educ + exper + female | firm_id, data = dat)
```

### Build the regression table

```{r regtab}
tab <- regtab(
  models    = list("(1)" = m1, "(2)" = m2),
  coef_map  = c(
    educ   = "Years of education",
    exper  = "Experience (years)",
    female = "Female"
  ),
  fe_labels = c(firm_id = "Firm FE")
)
```

### Console output

```{r print}
print(tab)
```

### LaTeX output

```{r latex}
to_latex(tab)
```

### Excel output

```{r excel, eval = FALSE}
to_excel(tab, path = "table1.xlsx")
```

## Full documentation

See the vignette for a complete walkthrough of all features including
`col_groups`, `add_rows`, `se_format`, factor variables, and IV models:

```r
vignette("getting-started", package = "exportreg")
```
