---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# exportreg

exportreg builds publication-ready regression tables for economists, with
first-class fixest support and Excel and LaTeX as priority output formats.

## Installation

```r
# install.packages("remotes")
remotes::install_github("viclzrz/exportreg")
```

## Minimal example

`regtab()` accepts a named list of model objects — mix `lm` and `feols`
freely. The names become the column headers.

### Data and models

```{r models, message = FALSE}
library(exportreg)
library(fixest)

set.seed(42)
n <- 500

# Instrument correlated with education
instrument <- rnorm(n)
educ       <- round(12 + 2 * instrument + rnorm(n), 0)
educ       <- pmax(6, pmin(20, educ))
exper      <- sample(1:30, n, replace = TRUE)
firm_id    <- sample(1:50,  n, replace = TRUE)

# True wage equation
firm_fe    <- rnorm(50)[firm_id]
wage       <- exp(
  0.08 * educ +
  0.02 * exper +
  firm_fe +
  rnorm(n, sd = 0.3)
)

df <- data.frame(wage, educ, exper, firm_id, instrument)

m1 <- lm(log(wage) ~ educ + exper,
         data = df)
m2 <- feols(log(wage) ~ educ + exper | firm_id,
            data = df, cluster = ~firm_id)
m3 <- feols(log(wage) ~ exper | firm_id |
            educ ~ instrument,
            data = df, cluster = ~firm_id)
```

### Example 1 — standard errors in parentheses

`m1` uses IID standard errors; `m2` and `m3` are clustered at the firm
level. `regtab()` detects both SE types and builds the note automatically.
`coef_map` aligns the Education row across all three columns: OLS and FE
report the coefficient as `educ`, the IV second stage as `fit_educ` — both
map to the same display label.

```{r tab1}
tab <- regtab(
  models         = list("(1) OLS" = m1,
                        "(2) FE"  = m2,
                        "(3) IV"  = m3),
  fe_labels      = c("firm_id" = "Firm"),
  cluster_labels = c("firm_id" = "Firm"),
  depvar_labels  = c("log(wage)" = "ln(wage)"),
  coef_map       = c("educ"     = "Education",
                     "fit_educ" = "Education",
                     "exper"    = "Experience")
)
```

```{r latex1, comment = ""}
to_latex(tab)
```

The significance note reflects the mixed SE setup: column (1) uses IID
standard errors, while columns (2) and (3) are clustered at the Firm level.
The Firm FE row shows No / Yes / Yes, and column (3) includes a KP F-stat
row from the first stage.

### Example 2 — t-statistics in brackets

Pass `se_format = "tstat"` to show absolute t-statistics in brackets instead
of standard errors in parentheses. The note updates automatically.

```{r tab2}
tab_t <- regtab(
  models         = list("(1) OLS" = m1,
                        "(2) FE"  = m2,
                        "(3) IV"  = m3),
  fe_labels      = c("firm_id" = "Firm"),
  cluster_labels = c("firm_id" = "Firm"),
  depvar_labels  = c("log(wage)" = "ln(wage)"),
  coef_map       = c("educ"     = "Education",
                     "fit_educ" = "Education",
                     "exper"    = "Experience"),
  se_format      = "tstat"
)
```

```{r latex2, comment = ""}
to_latex(tab_t)
```

### Example 3 — Excel output

`to_excel()` writes a formatted `.xlsx` file using `openxlsx2` (no Java
required). Column widths are auto-fitted and headers are bolded.

```{r excel, eval = FALSE}
to_excel(tab, file = "table1.xlsx")
# to_excel(tab, file = "table1.xlsx", raw = TRUE)
```

## Full documentation

For a full walkthrough including multi-panel tables and all available
arguments, see the vignette:

```r
vignette("getting-started", package = "exportreg")
```
