---
title: "Getting Started with exportreg"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with exportreg}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", echo = TRUE)
library(exportreg)
```

`exportreg` turns a named list of model objects into a formatted regression
table that can be printed to the console or exported to Excel or LaTeX.  This
vignette walks through the main features using the built-in `mtcars` and
`iris` datasets, plus a small synthetic panel for the fixed-effects and
IV examples.

---

## 1  Basic OLS with mtcars

Pass a **named** list of models to `regtab()`. The names become the column
headers.

```{r ols-models}
m1 <- lm(mpg ~ wt + hp,        data = mtcars)
m2 <- lm(mpg ~ wt + hp + disp, data = mtcars)
```

### Renaming and grouping columns

`coef_map` renames raw coefficient names to display labels.  `col_groups`
produces a spanning header row in the LaTeX output.

```{r ols-table}
coef_labels <- c(
  "(Intercept)" = "Constant",
  "wt"          = "Weight (1,000 lbs)",
  "hp"          = "Horsepower",
  "disp"        = "Displacement (cu.in.)"
)

extra_rows <- data.frame(
  label = c("Dataset", "Outcome"),
  "(1)" = c("mtcars", "mpg"),
  "(2)" = c("mtcars", "mpg"),
  check.names = FALSE,
  stringsAsFactors = FALSE
)

tab_ols <- regtab(
  models     = list("(1)" = m1, "(2)" = m2),
  coef_map   = coef_labels,
  add_rows   = extra_rows,
  col_groups = c("(1)" = "Miles per Gallon", "(2)" = "Miles per Gallon")
)

print(tab_ols)
```

`add_rows` appends arbitrary labelled rows below the statistics block —
useful for noting the dataset, clustering scheme, or bandwidth.

### LaTeX output

```{r ols-latex}
to_latex(tab_ols)
```

`col_groups` is rendered as a `\multicolumn` spanning header with `\cmidrule`
rules in the LaTeX output.

---

## 2  Factor variables with iris

When a model includes a factor variable, `factor_labels` groups the dummy
coefficients under a single indented header row.

```{r iris-lm}
m_iris <- lm(
  Sepal.Length ~ Petal.Length + Petal.Width + Species,
  data = iris
)

tab_iris <- regtab(
  list("(1)" = m_iris),
  coef_map = c(
    "(Intercept)"       = "Constant",
    "Petal.Length"      = "Petal length",
    "Petal.Width"       = "Petal width",
    "Speciesversicolor" = "versicolor",
    "Speciesvirginica"  = "virginica"
  ),
  factor_labels = c("Species" = "Species (ref: setosa)")
)

print(tab_iris)
to_latex(tab_iris)
```

`is_factor_header = TRUE` rows are printed without a standard-error line and
sort immediately before their child coefficients.

### GLM on a binary outcome

`regtab()` also accepts `glm` objects.

```{r iris-glm}
iris2            <- iris
iris2$virginica  <- as.integer(iris$Species == "virginica")

m_glm <- glm(
  virginica ~ Petal.Length + Petal.Width,
  data   = iris2,
  family = binomial()
)

tab_glm <- regtab(
  list("(1)" = m_glm),
  coef_map = c(
    "(Intercept)"  = "Constant",
    "Petal.Length" = "Petal length",
    "Petal.Width"  = "Petal width"
  )
)

print(tab_glm)
```

---

## 3  Fixed effects and clustered SEs

`fixest::feols()` is the primary model class. Fixed-effect variables are
detected automatically from `model$fixef_vars` and displayed in a separate
block. Standard errors clustered by `cluster = ~group` trigger a `Clusters`
row in the statistics block.

```{r fe-data}
set.seed(42)
n_groups <- 20L
n_per    <- 15L
group_id <- rep(seq_len(n_groups), each = n_per)
x1 <- rnorm(n_groups * n_per)
x2 <- rnorm(n_groups * n_per)
y  <- 0.5 * x1 - 0.3 * x2 +
      rep(rnorm(n_groups, sd = 0.5), each = n_per) +
      rnorm(n_groups * n_per, sd = 0.4)

panel_df <- data.frame(y = y, x1 = x1, x2 = x2, group = group_id)
```

```{r fe-models}
m_fe1 <- fixest::feols(y ~ x1      | group, cluster = ~group, data = panel_df)
m_fe2 <- fixest::feols(y ~ x1 + x2 | group, cluster = ~group, data = panel_df)

tab_fe <- regtab(
  models    = list("(1)" = m_fe1, "(2)" = m_fe2),
  fe_labels = c("group" = "Group FE"),
  drop      = "Intercept"
)

print(tab_fe)
to_latex(tab_fe)
```

---

## 4  IV estimation

Add a second `|` separator to instrument an endogenous regressor.  The
statistics block includes a `KP F-stat` row (Kleibergen–Paap weak-instrument
F-statistic) when the model is estimated by 2SLS.

```{r iv}
panel_df$z <- -0.6 * x1 + rnorm(n_groups * n_per, sd = 0.8)

m_iv <- fixest::feols(
  y ~ x2 | group | x1 ~ z,
  cluster = ~group,
  data    = panel_df
)

tab_iv <- regtab(
  models    = list("OLS" = m_fe2, "2SLS" = m_iv),
  fe_labels = c("group" = "Group FE"),
  drop      = "Intercept"
)

to_latex(tab_iv, format = "full")
```

`format = "full"` wraps the `tabular` environment in a complete LaTeX
document with `\usepackage{booktabs}`, ready to compile standalone.

---

## 5  Multi-panel tables

Pass a named list of `regtab_table` objects to `panels` to stack results
vertically.  All panels must share identical column names.  Here we split
`mtcars` by transmission type.

```{r panels}
auto_df   <- mtcars[mtcars$am == 0, ]
manual_df <- mtcars[mtcars$am == 1, ]

make_lm_list <- function(df) {
  list(
    "(1)" = lm(mpg ~ wt,      data = df),
    "(2)" = lm(mpg ~ wt + hp, data = df)
  )
}

short_map <- c(
  "(Intercept)" = "Constant",
  "wt"          = "Weight",
  "hp"          = "Horsepower"
)

tab_auto   <- regtab(make_lm_list(auto_df),   coef_map = short_map)
tab_manual <- regtab(make_lm_list(manual_df), coef_map = short_map)

tab_panels <- regtab(
  panels = list("Automatic" = tab_auto, "Manual" = tab_manual)
)

print(tab_panels)
```

Each panel gets a bold header row ("Panel A: Automatic", "Panel B: Manual")
and the statistics block accumulates rows from both panels.

---

## Custom tables from pre-computed estimates

`tex_table()` Mode B is for cases where results do not come from R model
objects — for example pre-computed estimates imported from a CSV, Stata
output, or bootstrap results.  Instead of passing a `regtab_table`, you
supply a character vector of pre-built row lines produced by the helper
functions (`tex_coef_row()`, `tex_se_row()`, `tex_stat_row()`,
`tex_panel()`, `tex_hline()`) and tell `tex_table()` how many data columns
the table has.  No model fitting is required.

### Single-panel example

```{r precomputed-setup}
set.seed(42)

# Pre-computed estimates (as if imported from a CSV or Stata output)
outcomes  <- c("Dropout", "Absent", "Conduct", "GPA (z)", "GPA math (z)")
b_treat   <- c(-0.012, -0.431,  0.008,  0.042,  0.071)
se_treat  <- c( 0.009,  0.318,  0.011,  0.038,  0.034)
p_treat   <- c( 0.187,  0.175,  0.468,  0.271,  0.038)
n_obs     <- c(1243L,  1243L,  1198L,  1201L,  1201L)
mean_ctrl <- c( 0.089,  4.832,  0.043,  0.000, -0.001)
```

```{r precomputed-basic}
tab <- tex_table(
  rows = c(
    tex_coef_row("Treatment", b = b_treat, p = p_treat),
    tex_se_row(se_treat),
    tex_hline(),
    tex_stat_row("Observations", n_obs, integer = TRUE),
    tex_stat_row("Control mean", mean_ctrl)
  ),
  ncols = 5,
  note  = paste("Standard errors in parentheses.",
                "*** p<0.01, ** p<0.05, * p<0.1")
)
```

`ncols = 5` tells `tex_table()` that there are five data columns (one per
outcome); the label column is added automatically.  The `note` argument
supplies the full footnote text — no automatic SE-type sentence is appended
in Mode B.

### Multi-panel example

Use `tex_panel()` to insert bold panel-header rows when stacking subgroups
vertically.

```{r precomputed-panels}
b_male    <- c(-0.008, -0.287,  0.003,  0.031,  0.089)
se_male   <- c( 0.011,  0.401,  0.014,  0.049,  0.044)
p_male    <- c( 0.468,  0.474,  0.812,  0.528,  0.044)

b_female  <- c(-0.019, -0.612, -0.001,  0.055,  0.051)
se_female <- c( 0.013,  0.471,  0.016,  0.052,  0.047)
p_female  <- c( 0.143,  0.194,  0.951,  0.291,  0.278)

tab_panels <- tex_table(
  rows = c(
    tex_panel("Panel A: Male students",   ncols = 5),
    tex_coef_row("Treatment", b = b_male, p = p_male),
    tex_se_row(se_male),
    tex_hline(),
    tex_panel("Panel B: Female students", ncols = 5),
    tex_coef_row("Treatment", b = b_female, p = p_female),
    tex_se_row(se_female),
    tex_hline(),
    tex_stat_row("Observations", n_obs, integer = TRUE),
    tex_stat_row("Control mean", mean_ctrl)
  ),
  ncols = 5,
  note  = paste("Standard errors in parentheses.",
                "*** p<0.01, ** p<0.05, * p<0.1")
)
```

### Writing to a file

Pass `file` to write the LaTeX source directly to disk:

```{r precomputed-file, eval=FALSE}
tex_table(
  rows = c(
    tex_coef_row("Treatment", b = b_treat, p = p_treat),
    tex_se_row(se_treat),
    tex_hline(),
    tex_stat_row("Observations", n_obs, integer = TRUE),
    tex_stat_row("Control mean", mean_ctrl)
  ),
  ncols = 5,
  note  = paste("Standard errors in parentheses.",
                "*** p<0.01, ** p<0.05, * p<0.1"),
  file  = "table_custom.tex"
)
```

---

## 6  Excel export

`to_excel()` writes to an `.xlsx` file using `openxlsx2` (no Java
dependency).  Header rows are bold with a bottom border, section separators
use thin top borders, and column widths are auto-fitted.

```{r excel}
f <- tempfile(fileext = ".xlsx")
to_excel(tab_fe, file = f, sheet = "Results")
file.remove(f)
```

The workbook is written to a temporary file and immediately removed so the
vignette leaves no artefacts on disk.  In practice, supply a real path:

```r
to_excel(tab_fe, file = "results/table1.xlsx", sheet = "Table 1")
```
